\documentclass[10pt,a4paper]{altacv}

\geometry{left=1cm,right=1cm,top=1.25cm,bottom=1.25cm,columnsep=1.2cm}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\usepackage{paracol}
% hyperref loaded by altacv.cls

\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}

\name{Chakit Bhandari}
\tagline{AI Full Stack Developer}
\personalinfo{%
  \location{Melbourne, VIC}
  \email{chakitbhandari22@gmail.com}
  \phone{+61 434 057 320}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\columnratio{0.65}
\begin{paracol}{2}

% LEFT COLUMN
\cvsection{Experience}

\cvevent{AI Engineer}{Heya Voice AI}{Aug 2025 - Present}{Melbourne, VIC}
\begin{itemize}
\item Developed AI-driven voice automation with LLM orchestration, enabling 24/7 customer interactions and reducing manual call handling by 80\%.
\item Built an internal CLI tool to streamline deployment and configuration of voice agents, improving reliability and operational efficiency.
\item Developed and maintained complex n8n workflows, enabling end-to-end automation for critical business processes.
\end{itemize}
\divider

\cvevent{Software Developer Intern}{Digital Asset Custody Solutions Pty Ltd.}{Jul 2025 - Oct 2025}{Melbourne, VIC}
\begin{itemize}
\item Designed and built the end-to-end architecture for a crypto pricing engine on \textbf{AWS}, supporting real-time pricing for 20+ digital assets.
\item Integrated 5+ external market data providers to deliver reliable, low-latency pricing data feeds.
\item Developed serverless pipelines (API Gateway, AWS Lambda, RDS), reducing infrastructure overhead by 45\%.
\end{itemize}
\divider

\cvevent{Software Engineer}{Film Never Die}{Nov 2024 - Feb 2025}{Melbourne, VIC}
\begin{itemize}
\item Contributed to a groundbreaking \textbf{SaaS} product, enabling clients to save up to \$30,000 annually through optimized workflows.
\item Developed a Mobile app using \textbf{Flutter} for fast, user-friendly image access, replacing legacy systems like Dropbox.
\item Hosted images ranging from 5MB to 50MB on \textbf{CloudFront CDN} for faster access and efficient delivery to global users.
\end{itemize}
\divider

\cvevent{Software Developer}{Fresh Prints}{Jun 2023 -- Aug 2023}{Remote}
\begin{itemize}
\item Developed Customer Portal features, enabling direct client ordering and improving user experience.
\item Built a PDF image extraction API and migrated it to a \textbf{serverless AWS Lambda} architecture, reducing operational costs by 96\%.
\item Containerized services using \textbf{Docker} to improve scalability and reduce OS dependencies across deployment environments.
\end{itemize}

\switchcolumn

% RIGHT COLUMN
\cvsection{Education}

\cvevent{Master's of Information Technology}{RMIT University, Melbourne}{2024 - 2025}{}

\vspace{0.1cm}

\cvsection{Skills}

\cvtag{Problem Solving}
\cvtag{TypeScript}
\cvtag{Node.js}
\cvtag{React}
\cvtag{AWS}
\cvtag{LLMs}

\vspace{0.1cm}

\cvsection{Links}

\cvtag{\href{https://www.linkedin.com/in/chakit-bhandari}{\textbf{LinkedIn}}}
\cvtag{\href{https://github.com/Chakit22}{\textbf{GitHub}}}
\cvtag{\href{https://leetcode.com/Chakit_Bhandari}{\textbf{LeetCode}}}

\vspace{0.1cm}

\cvsection{Achievements}

\begin{itemize}
\item Secured 1st place in AI Agents Beginner Hackathon, presenting at Microsoft Office, Melbourne.
\item Achieved 3rd rank out of 200 participants in the O(NlogN) University event.
\end{itemize}

\vspace{0.1cm}

\cvsection{Projects}

\cvevent{Forge -- AI Learning Assistant}{\href{https://github.com/Chakit22}{GitHub}}{}{Team Project}
\begin{itemize}
\item Built an \textbf{AI-powered} learning tool with smart summaries, quizzes, mindmaps (React Flow), and speech-to-text notes.
\item Integrated \textbf{OpenAI GPT-4o}, \textbf{Weaviate} for vector DB, and \textbf{Whisper} for transcription services.
\item Tech Stack: \textbf{Next.js}, \textbf{GPT-4o}, \textbf{Weaviate}, \textbf{Whisper}, \textbf{Vercel} for full-stack development.
\end{itemize}

\end{paracol}

\end{document}