\documentclass[10pt,a4paper]{altacv}

\geometry{left=1cm,right=1cm,top=1.25cm,bottom=1.25cm,columnsep=1.2cm}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}
\usepackage{paracol}
% hyperref loaded by altacv.cls

\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}

\name{Chakit Bhandari}
\tagline{AI Full Stack Developer}
\personalinfo{%
  \location{Melbourne, VIC}
  \email{chakitbhandari22@gmail.com}
  \phone{+61 434 057 320}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\columnratio{0.65}
\begin{paracol}{2}

% LEFT COLUMN
\cvsection{Experience}

\cvevent{AI Engineer}{Heya Voice AI}{Aug 2025 - Present}{Melbourne, VIC}
\begin{itemize}
\item Built AI-driven voice automation systems using LLM orchestration and workflow automation to enable 24/7 intelligent customer interactions and reduce manual call handling by upto 80\%.
\item Built an internal CLI tool to streamline deployment and configuration of voice agents, improving reliability.
\item Developed and maintained complex n8n workflows, enabling end-to-end automation.
\end{itemize}
\divider

\cvevent{Software Developer Intern}{Digital Asset Custody Solutions Pty Ltd.}{Jul 2025 - Oct 2025}{Melbourne, VIC}
\begin{itemize}
\item Designed and built the end-to-end architecture for a crypto pricing engine on AWS, supporting real-time pricing for 20+ digital assets.
\item Integrated 5+ external market data providers to deliver reliable, low-latency pricing data.
\item Developed serverless pipelines using API Gateway, AWS Lambda, and RDS, reducing infrastructure overhead by 45\% while maintaining secure and scalable data flows.
\end{itemize}
\divider

\cvevent{Software Engineer}{Film Never Die}{Nov 2024 - Feb 2025}{Melbourne, VIC}
\begin{itemize}
\item Worked on a groundbreaking SaaS product helping clients save up to \$30,000 annually.
\item Developed a Mobile app using Flutter for fast, user-friendly image access, replacing Dropbox.
\item Hosted images ranging from 5MB to 50MB on CloudFront CDN for faster access and efficient delivery.
\end{itemize}
\divider

\cvevent{Software Developer}{Fresh Prints}{Jun 2023 -- Aug 2023}{Remote}
\begin{itemize}
\item Developed Customer Portal features enabling direct client ordering.
\item Built a PDF image extraction API and migrated it to a serverless AWS Lambda architecture, reducing costs by 96\%.
\item Containerized services using Docker to improve scalability and reduce OS dependencies.
\end{itemize}

\switchcolumn

% RIGHT COLUMN
\cvsection{Education}

\cvevent{Master's of Information Technology}{RMIT University, Melbourne}{2024 - 2025}{}

\vspace{0.3cm}

\cvsection{Skills}

\cvtag{Problem Solving}
\cvtag{TypeScript}
\cvtag{Node.js}
\cvtag{React}
\cvtag{AWS}
\cvtag{LLMs}
\cvtag{AI Agents}

\vspace{0.3cm}

\cvsection{Links}

\cvtag{\href{https://www.linkedin.com/in/chakit-bhandari}{\textbf{LinkedIn}}}
\cvtag{\href{https://github.com/Chakit22}{\textbf{GitHub}}}
\cvtag{\href{https://leetcode.com/Chakit_Bhandari}{\textbf{LeetCode}}}

\vspace{0.3cm}

\cvsection{Achievements}

\begin{itemize}
\item Secured \textbf{1st} place in AI Agents Beginner Hackathon event organized by University and got a chance to present at \textbf{Microsoft Office, Melbourne}.
\item Bagged \textbf{3rd rank} out of \textbf{200} participants in \textbf{O(NlogN)} University event.
\end{itemize}

\vspace{0.3cm}

\cvsection{Certificates}

\begin{itemize}
\item AccioJob Coding Competition
\item CodeKaze
\end{itemize}

\vspace{0.3cm}

\cvsection{Coding Profiles}

\begin{itemize}
\item Solved \textbf{1000+} problems on various coding platforms.
\item Knight on Leetcode (Max Rating: \textbf{1944}), 3 star on Codechef.
\end{itemize}

\vspace{0.3cm}

\cvsection{Projects}

\cvevent{Forge -- AI Learning Assistant}{\href{https://github.com/Chakit22}{GitHub}}{}{Team Project}
\begin{itemize}
\item Built an AI-powered tool with smart summaries, quizzes, mindmaps (React Flow), and speech-to-text notes.
\item Integrated OpenAI GPT-4o, Weaviate for vector DB, and Whisper for transcription.
\item Tech Stack: Next.js, GPT-4o, Weaviate, Whisper, Vercel
\end{itemize}

\end{paracol}

\end{document}