%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Chakit Bhandari} \\ \vspace{1pt}
    \small AI Full Stack Developer \\ \vspace{4pt}
    \small \raisebox{-0.1\height}\faPhone\ +61 434 057 320 ~
    \href{mailto:chakitbhandari22@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{chakitbhandari22@gmail.com}} ~
    \href{https://www.linkedin.com/in/chakit-bhandari}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/chakit-bhandari}} ~
    \href{https://github.com/Chakit22}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Chakit22}}
    \vspace{-8pt}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{Full Stack Developer with experience building LLM-powered voice automation, serverless AWS architectures, and multi-agent AI systems. Proficient in TypeScript, Python, React, and Node.js. LeetCode Knight with \textbf{1000+} problems solved.}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Engineer}{Aug 2025 -- Present}
      {Heya Voice AI}{Melbourne, VIC}
      \resumeItemListStart
        \resumeItem{Built AI voice automation using LLM orchestration, reducing manual call handling by \textbf{80\%}.}
        \resumeItem{Developed an internal CLI tool for deploying and configuring voice agents.}
        \resumeItem{Maintained complex \textbf{n8n} workflows enabling end-to-end automation.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{Jul 2025 -- Oct 2025}
      {Digital Asset Custody Solutions Pty Ltd.}{Melbourne, VIC}
      \resumeItemListStart
        \resumeItem{Designed a crypto pricing engine on \textbf{AWS} supporting real-time pricing for \textbf{20+} digital assets.}
        \resumeItem{Integrated \textbf{5+} market data providers for reliable, low-latency pricing data.}
        \resumeItem{Built serverless pipelines with API Gateway, \textbf{Lambda}, and RDS, cutting infra costs by \textbf{45\%}.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Nov 2024 -- Feb 2025}
      {Film Never Die}{Melbourne, VIC}
      \resumeItemListStart
        \resumeItem{Shipped a SaaS image management platform saving clients up to \textbf{\$30,000} annually.}
        \resumeItem{Built a mobile app with \textbf{Flutter} for fast image access, replacing Dropbox.}
        \resumeItem{Served images (\textbf{5--50MB}) via \textbf{CloudFront} CDN for efficient delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{Jun 2023 -- Aug 2023}
      {Fresh Prints}{Remote}
      \resumeItemListStart
        \resumeItem{Developed Customer Portal features enabling direct client ordering.}
        \resumeItem{Built a PDF extraction API on serverless \textbf{AWS Lambda}, reducing costs by \textbf{96\%}.}
        \resumeItem{Containerized services with \textbf{Docker} to improve scalability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Medico-Legal RAG System} $|$ \emph{LangGraph, LangChain, FastAPI, Python}}{2025}
          \resumeItemListStart
            \resumeItem{Built a RAG pipeline for medico-legal reports using \textbf{LangGraph} and \textbf{FastAPI}.}
            \resumeItem{Implemented a query router selecting between three retrieval strategies.}
            \resumeItem{Reduced irrelevant data retrieval by \textbf{75\%} via targeted section extraction.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Atlas -- AI Travel Planner} $|$ \emph{LangGraph, Gemini, TypeScript, SerpApi}}{2025}
          \resumeItemListStart
            \resumeItem{Built a multi-agent travel assistant with \textbf{LangGraph} and \textbf{Gemini 2.5 Flash}.}
            \resumeItem{Integrated \textbf{SerpApi}, \textbf{OpenWeatherMap}, and \textbf{AviationStack} for live data.}
            \resumeItem{Shipped a streaming \textbf{TypeScript} CLI with session persistence and guardrails.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{StaffIQ -- Smart Academic Hiring Platform} $|$ \emph{Next.js, GraphQL, Express, Gemini AI}}{2025}
          \resumeItemListStart
            \resumeItem{Built an AI-powered recruitment platform with role-based auth and \textbf{Gemini AI} candidate ranking.}
            \resumeItem{Deployed \textbf{GraphQL} admin dashboard with \textbf{TypeORM} and MySQL for reporting.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Python, JavaScript} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, Express, FastAPI, Flutter, LangChain, LangGraph, GraphQL, RAG} \\
     \textbf{Cloud \& DevOps}{: AWS (Lambda, API Gateway, RDS, CloudFront), Docker, Vercel, n8n} \\
     \textbf{AI Tools}{: Claude Code, Cursor, v0, ChatGPT, GitHub Copilot} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master's of Information Technology}{2024 -- 2025}
      {RMIT University}{Melbourne, VIC}
  \resumeSubHeadingListEnd
\vspace{-4pt}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{1st Place} -- AI Agents Hackathon; presented at \textbf{Microsoft Office, Melbourne}. \\
     \textbf{3rd Rank} out of \textbf{200} participants in \textbf{O(NlogN)} University coding event. \\
     LeetCode Knight (Rating: \textbf{1944}), 3-star CodeChef. \\
    }}
 \end{itemize}

\end{document}
